---
title: 'Extracting data from Twitter for #machinelearningflashcards'
layout: post
tags: [rstats, r, image-processing, machine-learning]
output: 
  html_document: 
    self_contained: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.path = "{{ site.url }}/post_data/ml-flashcards-",
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

I'm a fan of [Chris Albon](https://chrisalbon.com/)'s recent project [#machinelearningflashcards](https://twitter.com/hashtag/machinelearningflashcards?src=hash) on Twitter where generalized topics and methodologies are drawn out with key takeaways. It's a great approach to sharing concepts about machine learning for everyone and a timely refresher for those of us who frequently forget algorithm basics.

I leveraged [Maëlle Salmon](https://github.com/maelle)'s recent blog post on the [*Faces of #rstats Twitter*](http://www.masalmon.eu/2017/03/19/facesofr/) heavily as a tutorial for this attempt at extracting data from Twitter to download the #Machinelearningflashcards.

Source Repo for this work: [jasdumas/ml-flashcards](https://github.com/jasdumas/ml-flashcards)
___

## Directions

- Load libraries:

For this project I used `rtweet` to connect the Twitter API to search for relevant tweets by the hash tag, `dplyr` to filter and pipe things, `stringr` to clean up the tweet description, and `magick` to process the images. 

Note: I previously ran into trouble when downloading [*ImageMagick*](https://www.imagemagick.org/script/index.php) and detailed the errors and approaches, if you fall into the same trap I did: [https://gist.github.com/jasdumas/29caf5a9ce0104aa6bf14183ee1e3cd8](https://gist.github.com/jasdumas/29caf5a9ce0104aa6bf14183ee1e3cd8)
```{r}
library(rtweet)
library(dplyr)
library(magick)
library(stringr)
library(kableExtra)
library(knitr)
```

- Get tweets for the hash tag and only curated tweets for Chris Albon's work: 
```{r}
ml_tweets <- search_tweets("#machinelearningflashcards", n = 500, include_rts = FALSE) %>% filter(screen_name == 'chrisalbon')
```

```{r}
mt <- ml_tweets[1:3,]

kable(mt, format = "html") %>%
  kable_styling(bootstrap_options = "striped", 
                full_width = F) 
```

- Get text within the tweet to add to the file name by removing the hash tag and URL link: 
```{r}
ml_tweets$clean_text <- ml_tweets$text
ml_tweets$clean_text <- str_replace(ml_tweets$clean_text,"#[a-zA-Z0-9]{1,}", "") # remove the hashtag
ml_tweets$clean_text <- str_replace(ml_tweets$clean_text, " ?(f|ht)(tp)(s?)(://)(.*)[.|/](.*)", "") # remove the url link
ml_tweets$clean_text <- str_replace(ml_tweets$clean_text, "[[:punct:]]", "") # remove punctuation
```

- Download images of the flashcards from the `media_url` column and append the file name from the cleaned tweet text description and save into a folder:
```{r}
save_image <- function(df){
  for (i in c(1:nrow(df))){
    image <- try(image_read(df$media_url[i]), silent = F)
  if(class(image)[1] != "try-error"){
    image %>%
      image_scale("1200x700") %>%
      image_write(paste0("data/", ml_tweets$clean_text[i],".jpg"))
  }
 
  }
   cat("Function complete...\n")
}
```

- Apply the function:
```{r}
save_image(ml_tweets)
```

At the end of this process you can view all of the #machinelearningflashcards in one place! Thanks to Chris Albon for his work on this, and I'm looking forward to re-running this script to gain additional knowledge from new #machinelearningflashcards that are developed in the future! 


